---
title: "MAFS5310 Homework #2" 
author: "XiaoLi_20925438" 
date: "9 Nov 2022"
output:
    rmdformats::readthedown: 
    self_contained: true 
    thumbnails: true 
    lightbox: true 
    gallery: false 
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functions to realize risk parity portfolio

## **Step 1**

-   **Load market data**

```{r message=FALSE, warning=FALSE}
library(portfolioBacktest)
library(xts)  # to manipulate time series of stock data
library(quantmod)  # to download stock data
library(PerformanceAnalytics)  # to compute performance measures

# download data from YahooFinance
stock_namelist <- c("AAPL", "AMD", "ADI",  "ABBV", "AEZS", "A",  "APD", "AA","CF")

prices <- xts()
for (i in 1:length(stock_namelist)) {
  tmp <- Ad(getSymbols(stock_namelist[i], from = "2014-01-01", to = "2016-12-31", auto.assign = FALSE))
  tmp <- na.approx(tmp, na.rm = FALSE)  # interpolate NAs
  prices <- cbind(prices, tmp)
}
colnames(prices) <- stock_namelist

tclass(prices) <- "Date"
# compute log-returns
X_log <- diff(log(prices))[-1]
X_lin <- (prices/lag(prices) - 1)[-1]

# number of stocks
N <- ncol(X_log) 

# number of days
T <- nrow(X_log)  

# compute mu
mu <- colMeans(X_log)

# compute sigma
Sigma <- cov(X_log)

# plot
plot(
    prices/rep(prices[1, ], 
    each = nrow(prices)), 
    col = rainbow10equal, 
    legend.loc = "topleft",
    main = "Normalized prices"
)
```

## **Step 2**

-   **Design a portfolio function using any package you find.**

-   **Compare it with your own implementation or from the course slides.**

### Function1: using package ***`portfolioBacktest`***

```{r}
library(portfolioBacktest)
library(riskParityPortfolio)

# RPP 
bt_RPP <- function(dataset, ...) {
    prices <- dataset$adjusted
    log_returns <- diff(log(prices))[-1]
    return(riskParityPortfolio(cov(log_returns))$w)
}
```

### Function2: your own ***`implementation`***

```{r}
bt_RPP_own <- function(dataset, ...) {
    prices <- dataset$adjusted
    N <- ncol(prices)
    X <- diff(log(prices))[-1]  # returns
    Sigma <- cov(X)
    
    # minimize the target function using "L-BFGS-B"
    Target = function(x)
    {
        x = matrix(c(x, 1-sum(x)))
        TRC = as.vector((Sigma %*% x) * x)
        return(sum(outer(TRC,TRC,"-")^2))
    }
    
    sol = optim(
        par = rep(1/N,N-1), 
        Target,
        method = "L-BFGS-B",
        lower = 0
    )
    w = c(sol$par, 1-sum(sol$par))
    return(w)
}
```

## **Step 3**

-   **Write some benchmark portfolios**

### MVP

```{r}
bt_MVP <- function(dataset, lmd = 0.5) {
    prices <- dataset$adjusted
    N <- ncol(prices)
    
    # returns
    X <- diff(log(prices))[-1]  
    
    # compute sigma
    Sigma <- cov(X)
    
    # compute mu
    mu <- colMeans(X)
    
    w <- Variable(nrow(Sigma))
    
    prob <- Problem(Maximize(t(mu) %*% w - lmd*quad_form(w, Sigma)),
                  constraints = list(w >= 0, sum(w) == 1))
    result <- solve(prob)
    return(as.vector(result$getValue(w)))
}
```

### IVP

```{r}
bt_IVP <- function(dataset, ...) {
    prices <- dataset$adjusted
    N <- ncol(prices)
    X <- diff(log(prices))[-1]  # returns
    Sigma <- cov(X)
    
    # portfolio design
    sigma <- sqrt(diag(Sigma))
    w <- 1/sigma
    w <- w/sum(w)
    return(w)
}
```

### MDP

```{r}
bt_MDP <- function(dataset, ...) {
    prices <- dataset$adjusted
    X <- diff(log(prices))[-1]  # returns
    Sigma <- cov(X)
    mu <- sqrt(diag(Sigma))
    
    w_ <- Variable(nrow(Sigma))
    prob <- Problem(Minimize(quad_form(w_, Sigma)),
                    constraints = list(w_ >= 0, t(mu) %*% w_ == 1))
    result <- CVXR::solve(prob)
    w <- as.vector(result$getValue(w_)/sum(result$getValue(w_)))
    names(w) <- colnames(Sigma)
    return(w)
}
```

## **Step 4**

#### **Back testing**

```{r message=FALSE, warning=FALSE}
library(CVXR)
# MVP
MVP <- function(mu, Sigma, lmd = 0.5) {
  w <- Variable(nrow(Sigma))
  prob <- Problem(Maximize(t(mu) %*% w - lmd*quad_form(w, Sigma)),
                  constraints = list(w >= 0, sum(w) == 1))
  result <- solve(prob)
  return(as.vector(result$getValue(w)))
}
w_MVP <- MVP(mu, Sigma)

# EWP
w_EWP <- rep(1/N, N)

# RPP
RPP <- function(prices) {
    log_returns <- diff(log(prices))[-1]
    return(riskParityPortfolio(cov(log_returns))$w)
}
w_RPP <- RPP(prices)

# RPP_own
RPP_own <- function(prices) {
    N <- ncol(prices)
    X <- diff(log(prices))[-1]  # returns
    Sigma <- cov(X)
    
    # minimize the target function using "L-BFGS-B"
    Target = function(x)
    {
        x = matrix(c(x, 1-sum(x)))
        TRC = as.vector((Sigma %*% x) * x)
        return(sum(outer(TRC,TRC,"-")^2))
    }
    
    sol = optim(
        par = rep(1/N,N-1), 
        Target,
        method = "L-BFGS-B",
        lower = 0
    )
    w = c(sol$par, 1-sum(sol$par))
    return(w)
}

w_RPP_own <- RPP_own(prices)


IVP <- function(prices, ...) {
    N <- ncol(prices)
    X <- diff(log(prices))[-1]  # returns
    Sigma <- cov(X)
    
    # portfolio design
    sigma <- sqrt(diag(Sigma))
    w <- 1/sigma
    w <- w/sum(w)
    return(w)
}
w_IVP <- IVP(prices)


MDP <- function(prices, ...) {
    X <- diff(log(prices))[-1]  # returns
    Sigma <- cov(X)
    mu <- sqrt(diag(Sigma))
    
    w_ <- Variable(nrow(Sigma))
    prob <- Problem(Minimize(quad_form(w_, Sigma)),
                    constraints = list(w_ >= 0, t(mu) %*% w_ == 1))
    result <- CVXR::solve(prob)
    w <- as.vector(result$getValue(w_)/sum(result$getValue(w_)))
    names(w) <- colnames(Sigma)
    return(w)
}
w_MDP <- MDP(prices)

# put together all portfolios
w_all <- cbind(w_MVP,w_EWP,w_RPP,w_RPP_own,w_IVP,w_MDP)
rownames(w_all) <- colnames(X_lin)
colnames(w_all) <- c("MVP","EWP","RPP","RPP_own","IVP","MDP")
w_all
```

#### **Portfolio allocation**

```{r}
# plot
barplot(
    t(w_all),
    col = rainbow8equal[1:6],
    main = "Portfolio allocation",
    xlab = "stocks",
    ylab = "dollars",
    beside = TRUE,
    legend = colnames(w_all)
)
```

#### **risk contribution**

```{r}
# compute risk contributions
risk_all <- cbind(
    "MVP"        = as.vector(w_MVP * (Sigma %*% w_MVP)),
    "EWP"        = as.vector(w_EWP * (Sigma %*% w_EWP)),
    "RPP"        = as.vector(w_RPP * (Sigma %*% w_RPP)),
    "RPP_own"    = as.vector(w_RPP_own * (Sigma %*% w_RPP_own)),
    "IVP"        = as.vector(w_IVP * (Sigma %*% w_IVP)),
    "MDP"        = as.vector(w_MDP * (Sigma %*% w_MDP))
)
rownames(risk_all) <- colnames(X_lin)
RRC_all <- sweep(risk_all, MARGIN = 2, STATS = colSums(risk_all), FUN = "/")  # normalize each column

# plot
barplot(t(RRC_all), col = rainbow8equal[1:6],
        main = "Relative risk contribution", xlab = "stocks", ylab = "risk", beside = TRUE, 
        legend = colnames(RRC_all))
```

#### **risk contribution: RPP with own implementation**

```{r}
# compute risk contributions
risk_all <- cbind(
    "RPP"        = as.vector(w_RPP * (Sigma %*% w_RPP)),
    "RPP_own"    = as.vector(w_RPP_own * (Sigma %*% w_RPP_own))
)
rownames(risk_all) <- colnames(X_lin)
RRC_all <- sweep(risk_all, MARGIN = 2, STATS = colSums(risk_all), FUN = "/")  # normalize each column

# plot
barplot(t(RRC_all), col = rainbow8equal[1:2],
        main = "Relative risk contribution", xlab = "stocks", ylab = "risk", beside = TRUE, 
        legend = colnames(RRC_all))
```

## Step 5

From the portfolio allocation graph we can see that:

-   Since APPLE and AMD's stock price is robust during the time interval(Jul 01 2016 - Dec 30 2016). The results from Markowitz Portfolio tells us that we should invest most of our money into AMD and APPLE, because in that way we can enjoy a max utility. However, about the rest of the stocks, due to their bad performance, we should avoid investing them.

From the risk contribution graph we can see that:

-   our own implementation dose not keep tracking of the RPP package, instead it suggests that we should distribute a great majority of risk to AEZS which perform badly and barely produce any profit during the time interval. However, AEZS's graph in the return graph is unique since others don't behave like that(fall almost to the ground). There must be some error in our own implementation. As I change the optimization function(instead using ***`L-BFGS-B`***, using the **default** one), the result turned back to what I expected. The most likely reasons is that the solution falls into a local min, which needs other optimize function to get a better solution.

    ```{r}
    # RPP_own
    RPP_own <- function(prices) {
        N <- ncol(prices)
        X <- diff(log(prices))[-1]  # returns
        Sigma <- cov(X)
        
        # minimize the target function using "L-BFGS-B"
        Target = function(x)
        {
            x = matrix(c(x, 1-sum(x)))
            TRC = as.vector((Sigma %*% x) * x)
            return(sum(outer(TRC,TRC,"-")^2))
        }
        
        sol = optim(
            par = rep(1/N,N-1), 
            Target
            #method = "L-BFGS-B",
            #lower = 0
        )
        w = c(sol$par, 1-sum(sol$par))
        return(w)
    }

    w_RPP_own <- RPP_own(prices)

    # compute risk contributions
    risk_all <- cbind(
        "RPP"        = as.vector(w_RPP * (Sigma %*% w_RPP)),
        "RPP_own"    = as.vector(w_RPP_own * (Sigma %*% w_RPP_own))
    )
    rownames(risk_all) <- colnames(X_lin)
    RRC_all <- sweep(risk_all, MARGIN = 2, STATS = colSums(risk_all), FUN = "/")  # normalize each column

    # plot
    barplot(t(RRC_all), col = rainbow8equal[1:2],
            main = "Relative risk contribution", xlab = "stocks", ylab = "risk", beside = TRUE, 
            legend = colnames(RRC_all)) 
    ```
